Phenomenological Robotics

### 2011-12-22 draft.tex
Started writing about affordances in robotics.

>>>>

% 3.B. Affordances vs. Robotics (Rome's book).
% (Source: Thesis journal, pages 130 to 139, 16/03/2011).
% Note: I believe citing examples of affordances in Robotics is a must here.
% A bridge between the former subject (Todes-Kuipers-Lemmen) might be necessary,
% or even a new section.

% Note: the next reference being focused on the coupling between more than one
% robot, I'm not sure it fits completely here (in affordances) instead of
% somewhere else (in coupling) or nowhere at all.
Hafner and Kaplan~\cite{hafner2008} present the concept of \emph{interpersonal
maps}, creating a representation space that allows one's behavior to the
behavior of others. To validate their approach, they perform a set of
experiments with four-legged robots either acting alone or engaged in imitation.

Hertzberg et al.~\cite{hertzberg2008} discuss the perception of
\emph{navegability} as an affordance. He presents \emph{navegability maps} as an
example, and classify them as \emph{semantic maps}. They defend that

\begin{quotation}
  [E]very efficient robot control system includes highly tuned sensor data
  processing modules \dots to perceive \dots robot-environment relations that
  are necessary for the robot's intended function.
\end{quotation}

They leave, however, the insight to develop each of this processing modules to
the designer, making it impractical for robots that should work in unstructured,
dynamic environments.

Raubal and Maratz~\cite{raubal2008} propose a functional model based on an
extended theory of affordances. They demonstrate its applicability with two
different robot scenarios, where the objects ``tell'' the robot what they can be
used for.

Sutton and Start~\cite{sutton2008} implement a system that segments images in
\emph{affordances} instead of \emph{objects}. The training dataset is labeled is
labeled manually. Even though, their algorithm is able to evaluate if a surface
``provides stable support'' (like a chair), ``confirms graspability'' (like any
graspable object) or ``confirms containment'' (like a cup). One of their results
worth mentioning is the labelling of an upside-down garbage can as ``sittable''.
